The globular cluster system of the Auriga simulations

### 2019-12-09 response_to_referee.tex

\begin{document}

\section*{Introduction (of referee report)}
``The results of the paper clearly demonstrate that the technique of simulating
stellar clusters in cosmological hydrodynamical simulations by tagging stellar
particles based on their ages does not reproduce key properties of observed GC 
systems in the Milky Way and M31. However, the authors do not state this conclusion
anywhere''.

We feel that our conclusion would be too strongly phrased if we would generalise 
our results obtained using the Auriga simulations to cosmological simulations 
in general. Indeed, we do find that age-selected stellar particles do not 
reproduce key properties of observed GC systems in the Milky Way and M31. However,
our results might reflect characteristics that are specific to Auriga, 
e.g. that the galaxy formation model overmixes metals at early times. 
Therefore we did add a final bulletpoint to our conclusion to clarify the above, 
but we limit the scope to the Auriga simulations.

\section*{General comments about style}
\begin{itemize}
\item
\item
\item
\item
\item I replaced `Sec.' by `Section' to refer to sections in the present work.
Moreover, I changed `Sec.' to `section' to refer to a section in one of the references.
\item All acronyms are introduced the first time they appear in the text
(MW, M31, GC, GCS, YMC, ISM, SN, AGB, DM, and Au). The subset thereof that appears 
in the abstract is also introduced the first time it appears.
\item The colour palette has been updated to improve colourblind-friendliness.
\item We no longer use blue and red to prevent confusion because they are 
typically used for metal-poor and metal-rich populations.
\end{itemize}

@@

\section*{Major comments and concerns}
\begin{itemize}
\item Item
\end{itemize}

\section*{Additional major comments}
\begin{itemize}
\item We normalise the Auriga simulations by the virial radius of the
dark matter halo to compensate for scatter between different simulation runs. We
deliberately chose for $r_{vir}$ because there are several stellar length scales
that could be used (e.g. the effective radius of the bulge, the radial scalelength
or vertical scaleheight of the disk, the optical radius, the extent of the stellar 
halo, etc). The simulations show a wide variety between properties of the Auriga
galaxies with little correlation between these different stellar length scales.
The mean virial radius of Auriga L4 is 299.67 $\pm$ 19.41 kpc.
\item Item
\end{itemize}

\section*{Comments for each section}
\subsection*{Introduction}
\begin{itemize}
\item Item
\end{itemize}

\subsection*{Sect. 2 -}
\begin{itemize}
\item Item
\end{itemize}

\subsection*{Sect. 3 -}
\begin{itemize}
\item Item 
\end{itemize}

\subsection*{Sect. 4 -}
\begin{itemize}
\item
\item Figure 4 - now has a vertical line to indicate the metallicity cut 
between metal-poor and metal-rich GC subpopulations in the Milky Way.
\item
\item
\item Figure 6: no changes were made for rescaling the galaxies (i.e. we still
use the virial radius)
\item Figure 5 and 7: shaded regions now show the 25-75th percentiles.
\item Figure 9: The values are removed from the masked upper right corner bins.
\item Figure 2,8,9: The values of the upper and right axes have been removed from
Figure 2 and 9 (observations) for clarity (rather than the suggestion to add 
axis labels and units). However, we did not mask these bins for Figure 8 (Auriga)
because it illustrates our finding that the simulations produce a considerable
amount of mass in GC candidates with low metallicities at large radii.
\end{itemize}

\subsection*{Sect. 5 -}
\begin{itemize}
\item Item
\end{itemize}

### 2019-12-09 AurigaGCS.tex
Update text to reflect changes in figures (colour palette and 25-75 percentitile range)

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GCSs of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candidates in green, and use a green dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (blue), and those that have been accreted (red).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We show the age-selected GC candidates as well as the 
accreted and {\it in~situ} subsets. The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep{Harris2001}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs. second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The green (blue)
        [red] crosses show the values calculated using all (only {\it in~situ})
        [only accreted] GC candidates. Green triangles indicate that all stars
        were used. The purple (magenta) cross denotes our calculation using all
        MW (M31) observations (which would be appropriate for a unimodal
        distribution). The black solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][page~38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW.
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
galaxies. The green crosses are to be compared to the purple (magenta) cross, 
which shows the mean value of all MW (M31) GCs. In addition, we show the metal-rich 
(metal-poor) population of the MW GCS using a solid (open) dot. We caution that
these literature values result from individual Gaussian fits to sub sets of the 
observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
points calculated using such an artificial cut for the simulated star particles.
It is interesting that the mean metallicities of the {\it in~situ} GC candidates 
appear roughly consistent with that of the metal-rich population of the MW despite 
the lack of such a metallicity cut, although the simulations show larger dispersions. 
The latter could simply be caused by the hard separation of the MW data into two 
groups, which means the range is smaller and the resulting dispersion lower. With 
regard to the M31 GCS, so far no definitive consensus has been reached
in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
but CR16 argues that the data, after removal of younger objects due to improved 
age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
hope that the simulated distribution is consistent with the lowest metallicity 
group in the M31 GCS. This is also true for the metal-poor population of the 
MW with a mean value of $-1.6$. The main result of this figure is 
that all Auriga L4 galaxies have metallicity distributions with (much) larger
mean values than what is observed for the MW and M31 GCS, and that we 
systematically find lower mean metallicities for the accreted GC candidates
than for those that have formed {\it in~situ}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (green dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median for all thirty Auriga L4 haloes with the $1\sigma$ interval around it 
(shaded regions, which shows the scatter between runs that have different initial 
conditions, thus, have unique merger histories). We chose to aggregate the data 
to indicate general trends that we find when the GC candidates are split up into
the accreted and {\it in situ} subsets, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
and we find that the mass at the peak lowers by roughly one dex. The mass budget 
of the GC candidates is dominated by the {\it in~situ} subpopulation above
[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW (M31) 
GCS in purple (magenta) and notice that the difference between the MW and M31 
distributions is substantially larger than the scatter between different Auriga 
galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
the MW does not.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{LogRgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the logarithm of radial distribution 
        of star particles in each of the thirty Auriga L4 haloes compared to
        the MW (M31) GCS shown in purple (magenta). The Auriga (M31) radii are 
        divided by $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied 
        by $r_{\text{vir,MW}}$ to compensate for different intrinsic sizes of
        the galaxies.
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We divide the Auriga radii by
$r_{\text{vir,Au}}$ and multiply by $r_{\text{vir,MW}}$ to compensate for the different
intrinsic sizes of the Auriga galaxies. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
standard deviation of $\log_{10}(r_{\text{gal}})$ of star particles in all Auriga
L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
GCs (which are to be compared to the green crosses), but solid (open) dot now
shows our calculation of the mean value of the `red' metal-rich (`blue` metal-poor) 
population. We split the radii up into the metal-rich/metal-poor groups by taking
a metallicity cut at [Fe/H]~=~-1 as is done in the literature.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        L4 simulations, where the Auriga (M31) radii are again divided by 
        $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied by 
        $r_{\text{vir,MW}}$. We show the median value of all Auriga haloes for all
        stars (green dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; green solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (blue solid), and those that 
        were accreted (red solid). Shaded regions indicate the $1\sigma$ 
        interval. The MW (M31) GCS is shown in purple (magenta). The middle 
        (bottom) panel shows the ratio of the simulated mass to the mass in the 
        MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed {\it in~situ} to the accreted population around
$10$~kpc. Again we show the mass ratio of the simulations compared to the MW 
and M31 GCS. We find a decreasing mass ratio with increasing radius
in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
to the accreted subpopulation. For the MW we notice that significantly
fewer GCs are found beyond $40$~kpc than for M31, and that accreted GC candidates
contribute mostly to the Auriga GCS at these radii. We further investigate a 
breakdown of the total mass in Auriga GC candidates into bins of both metallicity 
and radius in the following section.

>>>>

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GCSs of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candidates in beige, and use a beige dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (brown), and those that have been accreted (teal).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We show the age-selected GC candidates as well as the 
accreted and {\it in~situ} subsets. The top panel of Figure~\ref{fig:Au4-10and21_FeH} shows the MW 
and M31 GCSs, where we overplot a double Gaussian for the MW GCS by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep{Harris2001}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma-trim}.png}
    \caption{
        First vs. second central moment of the Auriga L4 metallicity distributions.
        Each cross (for a given colour) represents one simulation. The beige (brown)
        [teal] crosses show the values calculated using all (only {\it in~situ})
        [only accreted] GC candidates. Beige triangles indicate that all stars
        were used. The purple (magenta) cross denotes our calculation using all
        MW (M31) observations (which would be appropriate for a unimodal
        distribution). The purple solid (open) dots indicate the literature values
        of a bimodal Gaussian fit to the data \citep[values from][page~38]{1998gcs..book.....A},
        showing the metal-rich (metal-poor) component of the MW (separated at
        [Fe/H] = -1 as indicated by the vertical dotted magenta line).
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

We show the mean metallicity and standard deviation of all thirty Auriga L4 haloes
in Figure~\ref{fig:FeH_mu_sigma} to illustrate the behaviour for the full set of Auriga
galaxies. The beige crosses are to be compared to the purple (magenta) cross, 
which shows the mean value of all MW (M31) GCs. In addition, we show the metal-rich 
(metal-poor) population of the MW GCS using a solid (open) dot. We caution that
these literature values result from individual Gaussian fits to sub sets of the 
observational data cut at [Fe/H]~$= -1$. We do not include corresponding data 
points calculated using such an artificial cut for the simulated star particles.
It is interesting that the mean metallicities of the {\it in~situ} GC candidates 
appear roughly consistent with that of the metal-rich population of the MW despite 
the lack of such a metallicity cut, although the simulations show larger dispersions. 
The latter could simply be caused by the hard separation of the MW data into two 
groups, which means the range is smaller and the resulting dispersion lower. With 
regard to the M31 GCS, so far no definitive consensus has been reached
in the literature concerning uni- bi- or trimodality in the [Fe/H] distribution, 
but CR16 argues that the data, after removal of younger objects due to improved 
age classification, hints at three populations separated at [Fe/H]~$=-0.4$ and 
[Fe/H]~$ = 1.5$. None of the Auriga sub sets has a mean value that offers much 
hope that the simulated distribution is consistent with the lowest metallicity 
group in the M31 GCS. This is also true for the metal-poor population of the 
MW with a mean value of $-1.6$. The main result of this figure is 
that all Auriga L4 galaxies have metallicity distributions with (much) larger
mean values than what is observed for the MW and M31 GCS, and that we 
systematically find lower mean metallicities for the accreted GC candidates
than for those that have formed {\it in~situ}.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMFeH_withRatios-trim}.png}
    \caption{
        Mass-weighted metallicity distribution of star particles in the Auriga
        L4 simulations. We show the median value of all Auriga haloes for all
        stars (beige dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; beige solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (brown solid), and those that were accreted
        (teal solid). Shaded regions indicate the 25-75 percentile range. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:FeH}
    }
\end{figure}
We now turn to the second goal, which is to see whether sufficient total mass in 
GC candidates is produced by the Auriga simulations. To answer this question we plot
a mass-weighted metallicity distribution in Figure~\ref{fig:FeH}. We show the 
median for all thirty Auriga L4 haloes with the 25-75 percentile range 
(shaded regions, which shows the scatter between runs that have different initial 
conditions, thus, have unique merger histories). We chose to aggregate the data 
to indicate general trends that we find when the GC candidates are split up into
the accreted and {\it in situ} subsets, rather than selecting typical examples 
of individual (simulated) galaxies. Once again we notice that the peak metallicity 
shifts down from [Fe/H]~=~$0$ to [Fe/H]~=~$-0.6$ for GC candidates compared to all stars, 
and we find that the mass at the peak lowers by roughly one dex. The mass budget 
of the GC candidates is dominated by the {\it in~situ} subpopulation above
[Fe/H]~=~$-1$, and by the accreted subset below this value. We show the MW (M31) 
GCS in purple (magenta) and notice that the difference between the MW and M31 
distributions is substantially larger than the scatter between different Auriga 
galaxies, particularly around [Fe/H]~$=-1$. In addition, M31 does host 
(a handful of) GCs with [Fe/H]~$< -2.5$ as well as GCs with [Fe/H]~$ > 0$ while 
the MW does not.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{LogRgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the logarithm of radial distribution 
        of star particles in each of the thirty Auriga L4 haloes compared to
        the MW (M31) GCS shown in purple (magenta). The Auriga (M31) radii are 
        divided by $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied 
        by $r_{\text{vir,MW}}$ to compensate for different intrinsic sizes of
        the galaxies.
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
We repeat the analysis of the previous subsection for the distribution of
galactocentric radius instead of metallicity. We divide the Auriga radii by
$r_{\text{vir,Au}}$ and multiply by $r_{\text{vir,MW}}$ to compensate for the different
intrinsic sizes of the Auriga galaxies. We look for general trends present
in all Auriga L4 galaxies. Figure~\ref{fig:Rgc_mu_sigma} shows the mean and 
standard deviation of $\log_{10}(r_{\text{gal}})$ of star particles in all Auriga
L4 simulations. The purple (magenta) cross again shows the mean of the MW (M31)
GCs (which are to be compared to the beige crosses), but solid (open) dot now
shows our calculation of the mean value of the `red' metal-rich (`blue` metal-poor) 
population. We split the radii up into the metal-rich/metal-poor groups by taking
a metallicity cut at [Fe/H]~=~-1 as is done in the literature.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga
        L4 simulations, where the Auriga (M31) radii are again divided by 
        $r_{\text{vir,Au}}$ ($r_{\text{vir,M31}}$) and multiplied by 
        $r_{\text{vir,MW}}$. We show the median value of all Auriga haloes for all
        stars (beige dotted) and GC candidates (i.e. stars with
        age $>$~10~Gyr; beige solid). The latter sub set is further split up
        between stars that formed {\it in~situ} (brown solid), and those that 
        were accreted (teal solid). Shaded regions indicate the 25-75 percentile
        range. The MW (M31) GCS is shown in purple (magenta). The middle 
        (bottom) panel shows the ratio of the simulated mass to the mass in the 
        MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}
Figure~\ref{fig:Rgc} shows the mass-weighted radial distribution of the
Auriga L4 haloes. We notice a subtle peak around $10$~kpc for all star
particles that is not present for the GC candidates, indicating that the
stellar disc is no longer present when applying the latter selection criterion.
Furthermore, we find that the dominant contribution to the total mass in GC
candidates changes from those formed {\it in~situ} to the accreted population around
$10$~kpc. Again we show the mass ratio of the simulations compared to the MW 
and M31 GCS. We find a decreasing mass ratio with increasing radius
in the range $0.2$ to ${\sim}5$ kpc, followed by an increase attributed
to the accreted subpopulation. For the MW we notice that significantly
fewer GCs are found beyond $40$~kpc than for M31, and that accreted GC candidates
contribute mostly to the Auriga GCS at these radii. We further investigate a 
breakdown of the total mass in Auriga GC candidates into bins of both metallicity 
and radius in the following section.
